Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-02-16 main/doc/user_guide.tex
added user guide, removed redundant property file loading in pathconvert.xml, and other minor changes

%TODO: specify use of BDD's under efficiency in section 1 (overview)

\htmlmathitalic{0}
\htmltitle{User Guide}
\htmladdress{chord@cs.stanford.edu, \today}

\providecommand\Mdom{{\bf M}}
\providecommand\Idom{{\bf I}}
\providecommand\Vdom{{\bf V}}
\providecommand\Zdom{{\bf Z}}
\providecommand\Hdom{{\bf H}}
\providecommand\Edom{{\bf E}}
\providecommand\Fdom{{\bf F}}
\providecommand\Cdom{{\bf C}}
\providecommand\Tdom{{\bf T}}
\providecommand\Pdom{{\bf P}}
\providecommand\Sdom{{\bf S}}

@@

\providecommand\Chord{{Chord}}

@@

\title{Chord: A Static Analysis Framework for Java}
\author{Mayur Naik and Alex Aiken}
\date{\today}
\begin{document}
\maketitle
\texonly{\tableofcontents}

\texonly{\newpage}
\section{Overview}

\Chord\ is a static analysis framework for Java with an emphasis on the analysis of objects and concurrency.
It has the following characteristics:
\begin{enumerate}
\item
It is {\it stand-alone} in that it provides various off-the-shelf static analyses (e.g., may alias analysis, thread escape analysis, datarace analysis, deadlock analysis, etc.).
\item
It is {\it extensible} in that it allows users to build their own static analyses on top of the provided static analyses.
\item
It is {\it compositional} in that it enables different static analyses to coexist and interact with each other.
\item
It is {\it efficient} in that it
caches results computed by each static analysis so that they can be reused by other static analyses without re-computation.
\item
It is {\it flexible} in that it allows each static analysis to be expressed either declaratively as a Datalog program or imperatively as a Java program.
\end{enumerate}

@@

Before installing \Chord\ ensure that the following software is installed on your machine:

\begin{itemize}
\item
JDK 5 or higher (e.g., from
Sun\footnote{\xlink{{\tt http://java.sun.com/javase/downloads/index.jsp}}{http://java.sun.com/javase/downloads/index.jsp}}
or IBM\footnote{\xlink{{\tt http://www.ibm.com/developerworks/java/jdk/}}{http://www.ibm.com/developerworks/java/jdk/}}).

\item
Apache Ant (a Java build tool)\footnote{\xlink{{\tt http://ant.apache.org/}}{http://ant.apache.org/}}
\end{itemize}

Download the latest version of \Chord\ from \xlink{{\tt http://code.google.com/p/jchord/}}{http://code.google.com/p/jchord/}
(say {\tt chord-x.y.tar.gz}) and uncompress it in a suitable directory by running the following command:

\begin{verbatim}
tar xvzf chord-x.y.tar.gz
\end{verbatim}

This will create a directory structure with root directory {\tt chord-x.y/}.

\texonly{\newpage}
\section{Building Chord}

The root directory {\tt chord-x.y/} contains a {\tt build.xml} file which is interpreted by
Apache Ant (a Java build tool).
To see the various targets available run the following command in the root directory:

\begin{verbatim}
ant -p
\end{verbatim}

The default target {\tt compile} compiles \Chord.  So simply run the following command in the
root directory:

\begin{verbatim}
ant
\end{verbatim}

This will compile the \Chord\ {\tt .java} source files and store the {\tt .class} files
under the {\tt classes/} sub-directory of the root directory.

\texonly{\newpage}
\section{Running Chord}

@@

\begin{verbatim}
example/
    src/
        foo/
            Main.java
            ...
    classes/
        foo/
            Main.class
            ...
    lib/
        src/
            taz/
                ...
        jars/
            taz.jar
    chord/
        chord.properties
\end{verbatim}

The above structure is typical: the program's Java source files are under {\tt example/src/}, its class files
are under {\tt example/classes/}, the source and jar files of the libraries used by the program are under
{\tt example/lib/src/} and {\tt example/lib/jars/}, respectively, and finally {\tt example/chord/} is the directory
to which Chord will output its intermediate and final results.

Execute Chord on the above program by running the
following command in Chord's root directory {\tt chord-x.y/}:

\begin{verbatim}
ant -Dchord.work.dir=.../example/chord run
\end{verbatim}

where ``{\tt ...}'' denotes either the absolute path, or the path relative to Chord's root directory,
of the parent of directory {\tt example/}.
Chord will read the system properties specified in the file named {\tt chord.properties}
that it presumes exists in the directory specified
by system property {\tt chord.work.dir}
which in the above case is directory {\tt example/chord/}.
A sample such file for the above program is as follows:

\begin{verbatim}
chord.main.class=foo.Main
chord.class.path=../classes:../lib/classes/taz.jar
chord.src.path=../src:../lib/src
chord.out=log.txt
chord.err=log.txt
chord.serial.file=program.ser
chord.java.analysis.path=${chord.home.dir}/classes/main:
    ${chord.home.dir}/classes/downcast:${chord.home.dir}/src/dlog/monosite
chord.dlog.analysis.path=${chord.home.dir}/src/dlog/main:
    ${chord.home.dir}/src/dlog/downcast:${chord.home.dir}/src/dlog/monosite
chord.analyses=downcast-java,monosite-java
\end{verbatim}

System property {\tt chord.home.dir} specifies Chord's root directory
{\tt chord-x.y/}.
Every non-absolute location used in the value of any system property defined in the file
is taken to be relative to the directory specified by system
property {\tt chord.work.dir}.

Section \ref{sec-sys-prop} presents an exhaustive
listing of system properties that are recognized by \Chord.
Briefly:
\begin{itemize}
\item
{\tt chord.main.class} specifies the main class of the program
to be analyzed.
\item
{\tt chord.class.path} specifies the application classpath of the program to be analyzed (as opposed to the
JDK library classpath which consists of jar files such as {\tt rt.jar}
which are implicitly appended to the program's application classpath to yield the
complete program classpath).
\item
{\tt chord.out} and {\tt chord.err} specify the files (typically one and the same) to which the standard output and
standard error streams, respectively, must be redirected while running Chord.
\item
{\tt chord.serial.file} specifies the location of a file from (resp. to) which
the serialized form of the intermediate representation of the program to be analyzed must be loaded (resp. stored).
This option is provided because loading the serialized form is much faster than
constructing the intermediate representation of the program each time.
\item
{\tt chord.java.analysis.path} and {\tt chord.dlog.analysis.path} 
specify all program domains, program relations, and program analyses
to be included in the project and the
dependencies between them (see Section \ref{sec-tg}).
In the above case, they specify certain
 program domains, program relations, and program analyses
pre-defined in \Chord, in particular, all those in (1) Chord's standard library, (2) Chord's downcast safety
analysis, and (3) Chord's monomorphic call site analysis.
Users can also define their own
program domains, program relations, and program analyses and include them in the project.
\item
{\tt chord.analyses} is a space- or comma-separated list of the names of program domains,
program relations, and program analyses that must be run in that order.  In the above case,
these are downcast safety analysis, denoted {\tt downcast-java}, and monomorphic call site analysis,
denoted {\tt monosite-java}.
Both are program analyses pre-defined in \Chord\ 
but users can also include the names
of program domains, program relations, and program analyses they have defined and wish to run.
\end{itemize}

\texonly{\newpage}
\section{Specifying Program Scope}

\Chord\ takes as input a complete (i.e., closed) program with a main method.
The scope of the program must be specified in one of the
following ways:

\begin{itemize}
\item
Defining system property {\tt chord.serial.file} as
the location of a file containing in serialized form the intermediate representation
of the program generated by a previous run of \Chord.
\item
Defining system property {\tt chord.main.class} as the fully-qualified name
of the program's main class (e.g., {\tt foo.Main}) and system property
{\tt chord.class.path} as the program's application classpath.
\end{itemize}

The former option is provided because loading the serialized form
is much faster than constructing the intermediate representation
of the program each time.

\Chord\ first checks whether system property {\tt chord.serial.file} is defined.
If it is defined, then it further checks whether the file specified by it
exists.
If the file exists, then \Chord\ treats the file as a serialized form of
the intermediate representation of the program to be analyzed, and loads it.

If system property {\tt chord.serial.file} is not defined or if the file
specified by the property does not exist, then \Chord\ requires system properties
{\tt chord.main.class} and {\tt chord.class.path} 
to be defined, and uses them to
build an intermediate representation of the program (see Section \ref{sec-prog-build})
and perform source-to-source transformations on that representation
(see Section \ref{sec-prog-transform}) that simplify several program analyses.
Finally, if system property {\tt chord.serial.file} was defined but
specified a non-existent file, then \Chord\ creates the file and stores the
transformed intermediate representation of the program into the file in
serialized form so that it can be loaded in subsequent runs.

Defining system property {\tt chord.src.path} is optional.
It specifies the program's Java source path which provides the
locations of the program's {\tt .java} files so that, for instance, the
results of an analysis (which operates on the intermediate representation of
the program extracted from {\tt .class} files) can be mapped to the
program's {\tt .java} files and presented to the user for
manual inspection.

@@

Given the program's program's main class via system property {\tt chord.main.class} and the
program's application classpath via system property {\tt chord.class.path},
\Chord\ uses system property {\tt chord.program.builder.class} to locate the
builder to be used for building an intermediate representation of the program,
namely, an object of class {\tt chord.program.Program}.
By default, the value of this property is class {\tt chord.program.builders.SootProgramBuilder}
which uses the Soot Java compiler framework \cite{Soot}.
Any builder, however, must implement interface
{\tt chord.program.builders.IProgramBuilder}.

@@

\texonly{\newpage}
\section{Project Organization}

@@

\texonly{\newpage}
\section{Chord System Properties}
\label{sec-sys-prop}

@@

\item
{\tt chord.serial.file}

@@

The fully-qualified name of the main class (e.g., {\tt foo.Main}) of the
program to be analyzed.

This system property (and {\tt chord.class.path})
must be defined if system property {\tt chord.serial.file}
does not specify the file containing the serialized form of the intermediate representation
of the program to be analyzed.

\item
{\tt chord.class.path}

The application classpath of the program to be analyzed (as opposed to the
JDK library classpath which consists of jar files such as {\tt rt.jar}
which are implicitly appended to the program's application classpath to
yield the complete program classpath).

@@

This system property (and {\tt chord.main.class}) must
be defined if system property {\tt chord.serial.file}
does not specify the file containing the serialized form of the intermediate representation
of the program to be analyzed.

\item
{\tt chord.src.path}

@@

\item
{\tt chord.dlog.analysis.path}

@@

\item
{\tt chord.java.analysis.path}

@@

\item
{\tt chord.analyses}

>>>>

\htmlmathitalic{0}
\htmltitle{User Guide}
\htmladdress{mayur.naik@gmail.com, \today}

\providecommand\Mdom{{\bf M}}
\providecommand\Idom{{\bf I}}
\providecommand\Vdom{{\bf V}}
\providecommand\Zdom{{\bf Z}}
\providecommand\Hdom{{\bf H}}
\providecommand\Edom{{\bf E}}
\providecommand\Fdom{{\bf F}}
\providecommand\Cdom{{\bf C}}
\providecommand\Tdom{{\bf T}}
\providecommand\Pdom{{\bf P}}

@@

\providecommand\Chord{Chord}

@@

\title{Chord: A Static and Dynamic Program Analysis Framework for Java}
\author{Mayur Naik}
\date{\today}
\begin{document}
\maketitle
\texonly{\tableofcontents}

\texonly{\newpage}
\section{Introduction}

\Chord\ is a static and dynamic program analysis framework for Java.
It has the following key characteristics:

\begin{itemize}
\item
Stand-alone: various off-the-shelf program analyses are provided (e.g., may-alias, thread-escape, datarace, deadlock, etc.).
\item
Extensible: users can build their own program analyses on top of the provided ones.
\item
Compositional: each program analysis can be written independently and yet made to interact in complex ways with other program analyses.
\item
Efficient: results computed by each program analysis are cached for reuse by other program analyses without re-computation.
\item
Flexible: a broad range of program analyses can be expressed, including those
written imperatively in Java or declaratively in Datalog, summary-based as well as cloning-based context-sensitive analyses,
iterative refinement-based analyses, client-driven analyses, and combined static and dynamic analyses.
\end{itemize}

\Chord\ is intended for use by a broad range of users:

\begin{itemize}
\item
Software engineers: Programmers wanting to use program analyses in Chord to assist with software development and testing.
\item
Program analysis appliers: Researchers with possibly a limited program analysis background wanting to build applications on top of program analyses in Chord used as black boxes.
\item
Program analysis writers: Program analysis researchers wanting to implement and evaluate new program analysis algorithms.
\end{itemize}

\Chord\ is intended to work on a variety of platforms, including Linux, Windows, and MacOS.
It has been tested most extensively on Linux.

\Chord\ is open source software distributed under the \xlink{New BSD License}{http://www.opensource.org/licenses/bsd-license.php}.
Contributions from users are welcome and encouraged.

@@

Ensure that the following software is installed on your machine:

\begin{itemize}
\item
JDK 5 or higher, e.g. from \xlink{IBM}{http://www.ibm.com/developerworks/java/jdk/} or \xlink{Sun}{http://java.sun.com/javase/downloads/index.jsp}
\item
\xlink{Apache Ant}{http://ant.apache.org/}, a Java-based build tool
\item
a C++ compiler, e.g. \xlink{GCC}{http://gcc.gnu.org/}
\item
a Make utility, e.g. \xlink{GNU Make}{http://www.gnu.org/software/make/}
\item
\xlink{Cygwin}{http://www.cygwin.com/}, if it is Windows machine
\end{itemize}

Download the latest \Chord\ version from \xlink{here}{http://code.google.com/p/jchord/downloads/list} and uncompress it.

Directory {\tt chord/main} (henceforth called the main directory) contains a {\tt build.xml} file which is interpreted by Apache Ant.
To see the various targets available, run the following command in that directory:

\begin{quote}
\begin{verbatim}
prompt> ant
\end{verbatim}
\end{quote}

To compile \Chord, run the following command in the same directory:

\begin{quote}
\begin{verbatim}
prompt> ant compile
\end{verbatim}
\end{quote}

This will compile the following:
\begin{itemize}
\item
the Java source code of \Chord\ from {\tt chord/main/src/java/} to Java bytecode in {\tt chord/main/classes/}
\item
the C source code of BDD library \xlink{BuDDy}{http://buddy.sourceforge.net/} from {\tt chord/main/src/bdd/}
to a shared library in {\tt chord/main/lib/} ({\tt libbuddy.so} on Linux, {\tt buddy.dll} on Windows, and {\tt libbuddy.dylib} on MacOS);
this library is needed for executing program analyses written in Datalog using
\xlink{bddbddd}{http://bddbddb.sourceforge.net/} (a BDD-based Datalog solver).
\item
the C++ source code of the Chord instrumentation agent from {\tt chord/main/src/agent/} to a shared
library in {\tt chord/main/lib} ({\tt libchord\_instr\_agent.so} on Linux, {\tt chord\_instr\_agent.dll} on Windows,
and {\tt libchord\_instr\_agent.dylib} on MacOS); this agent is needed for building program scope dynamically
and for executing dynamic program analyses.
\end{itemize}

\texonly{\newpage}
\section{A Quick Tour}

@@

\begin{quote}
\begin{verbatim}
example/
    src/
        foo/
            Main.java
            ...
    classes/
        foo/
            Main.class
            ...
    lib/
        src/
            taz/
                ...
        jar/
            taz.jar
    chord.properties
\end{verbatim}
\end{quote}

The above structure is typical: the program's Java source files are under \verb+example/src/+,
its class files are under \verb+example/classes/+, the source and jar files of the libraries
used by the program are under \verb+example/lib/src/+ and \verb+example/lib/jar/+, respectively.

File \verb+chord.properties+ specifies properties to be passed to Chord (alternatively,
these properties may be passed on the command-line, in format \verb+-D<name>=<value>+).
A sample such file for the above program is as follows:

\begin{quote}
\begin{verbatim}
chord.main.class=foo.Main
chord.class.path=classes:lib/jar/taz.jar
chord.src.path=src:../lib/src
chord.run.ids=0,1
chord.args.0="-thread 1 -n 10"
chord.args.1="-thread 2 -n 50"
\end{verbatim}
\end{quote}

Each relative (instead of absolute) path element in the value of any property
named \verb+chord.<...>.path+ set in this file is converted to an absolute path element with respect
to the directory containing this file, which in the above case is \verb+example/+.

Section \ref{sec-sys-props} presents an exhaustive
listing of properties recognized by \Chord.
Here, we only describe those set in the above
sample \verb+chord.properties+ file:

\begin{itemize}
\item
\verb+chord.main.class+ specifies the fully-qualified name of the main class of the
program.
\item
\verb+chord.class.path+ specifies the classpath of the program.
The value of pre-defined property \verb+${sun.boot.class.path}+ is implicitly appended
to it.
\item
\verb+chord.src.path+ specifies the Java source path of the program.
All program analyses in Chord operate on Java bytecode (specified by \verb+chord.class.path+).
The only use of this property is to HTMLize the Java source files of the program so that the
results of program analyses can be reported at the Java source code level.
\item
\verb+chord.run.ids+ specifies a list of IDs to identify runs of the program.
It is used by dynamic program analyses to determine how many times the program must be run.
An additional use of this property is to allow specifying the command-line arguments to use
in the run having ID \verb+XXX+ via property \verb+chord.args.XXX+, as illustrated by
properties \verb+chord.args.0+ and \verb+chord.args.1+ in the above example.
\end{itemize}

Execute Chord on the above program by running the following command in Chord's main directory:

\begin{quote}
\begin{verbatim}
prompt> ant -Dchord.work.dir=<...>/example run
\end{verbatim}
\end{quote}

where \verb+<...>+ denotes either the absolute path, or the path relative to Chord's main directory,
of the parent of directory {\tt example/}.
System property \verb+chord.work.dir+ specifies the working directory during Chord's execution.

The above command causes Chord to load the \verb+chord.properties+ file if present.
The location of this file may be specified explicitly by property
\verb+chord.props.file+ on the above command line.
By default, it is \verb+${chord.work.dir}/chord.properties+.

In the above case, the above command does not do much beyond loading the sample \verb+chord.properties+ file.
For Chord to do something interesting, you need to set additional properties, either
on the above command line or in the \verb+chord.properties+ file, specifying the task(s)
Chord must perform.
All tasks are summarized in the ``Chord task properties" section at \ref{sec-sys-props}.
The two most common tasks, described next, are building program scope and
running program analyses.

\paragraph{Building Program Scope}

Chord computes program scope (i.e. reachable classes and methods of a given Java program) if property
\verb+chord.build.scope+ is set to \verb+true+.
The algorithm used to compute program scope is specified by 
properties \verb+chord.scope.kind+ and \verb+chord.reuse.scope+.

\begin{itemize}
\item
If property \verb+chord.reuse.scope+ is set to \verb+true+ and the files specified by
properties \verb+chord.classes.file+ and \verb+chord.methods.file+ exist,
then Chord regards those files as specifying the classes and methods, respectively,
to be regarded as reachable.  The format
of the classes file is a class name per line (e.g. \verb+foo.Main+).  The format
of the methods file is an entry of the form \verb+<method name>:<method descriptor>@<class name>+ per line,
specifying the method's name, the method's descriptor, and the method's declaring class
(e.g. \verb+main:([Ljava/lang/String;)V@foo.Main+).
Chord throws a runtime exception if the declaring class of a method in the methods file is not
specified in the classes file.
\item
If property \verb+chord.reuse.scope+ is set to \verb+false+ or the file specified by
property \verb+chord.classes.file+ or \verb+chord.methods.file+ does not exist,
then Chord computes program scope
using the algorithm specified by property \verb+chord.scope.kind+ and then
writes the classes and methods deemed reachable by that algorithm to those files.

The possible legal values of property \verb+chord.scope.kind+ are \verb+rta+ and \verb+dynamic+.
In both cases, Chord expects properties \verb+chord.main.class+ and \verb+chord.class.path+
to be set.
\begin{itemize}
\item
The \verb+rta+ value instructs Chord to compute the program scope statically using Rapid Type Analysis.
\item
The \verb+dynamic+ value instructs Chord to compute the program scope dynamically, by running the program
and observing using JVMTI the classes that are loaded at run-time.
The number of times the program is run and the command-line arguments to be supplied to
the program in each run is specified by properties \verb+chord.run.ids+ and
\verb+chord.args.XXX+ for each run ID \verb+XXX+.  By default, the program is run only once, using run ID \verb+0+,
and without any command-line arguments.
Only classes loaded in some run are regarded as reachable but {\it all} methods of each loaded class are regarded
as reachable regardless of whether they were invoked in the run.
The rationale behind this decision is to both reduce run-time overhead of JVMTI and to increase the
predictive power of program analyses performed using the computed program scope.
\end{itemize}
\end{itemize}

The default value of \verb+chord.reuse.scope+ is \verb+false+ and the default value of \verb+chord.scope.kind+
is \verb+rta+.
Finally, the default values of \verb+chord.classes.file+ and \verb+chord.methods.file+ are
\verb+${chord.out.dir}/classes.txt+ and \verb+${chord.out.dir}/methods.txt+, respectively,
where property \verb+chord.out.dir+ defaults to \verb+${chord.work.dir}/chord_output/+,
and property \verb+chord.work.dir+ defaults to the current working directory.

\paragraph{Running Program Analyses}

TODO

%chord.run.analyses
%List of names of program analyses to be run in order.
%chord.java.analysis.path	 path	 Classpath containing program analyses in Java (i.e. @Chord-annotated classes).	${chord.main.dir}/classes/
%chord.dlog.analysis.path	 path	 Path of directories containing program analyses in Datalog (i.e. *.datalog and *.dlog files).	${chord.main.dir}/src/main/dlog/
%chord.reuse.rels	 bool	 Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them.	false
%chord.publish.results	 bool	 Publish the results of program analyses in HTML.	true

%\texonly{\newpage}
%\section{Program Representation (todo)}

%TODO

%\texonly{\newpage}
%\section{Implementing Program Analyses (todo)}

%TODO

\texonly{\newpage}
\section{Chord System Properties}
\label{sec-sys-props}

The following properties are recognized by Chord.
The separator for list-valued properties can be either a blank space, a comma, a colon, or a semi-colon.

\begin{table}[htp]
%\caption{}
\xmlattributes*{table}{border="1"}
\begin{center}
\begin{tabular}{|l|lll|}
\hline
{\bf Property name} & {\bf Type} & {\bf Description} & {\bf Default value (if any)} \\
\hline
\multicolumn{4}{l}{{\bf Chord resource properties}} \\
\verb+chord.main.dir+ & location & \verb+main+ directory in Chord's installation. & \\
\hline
\verb+chord.lib.dir+ & location & Directory containing libraries needed by Chord. & \verb+${chord.main.dir}/lib/+ \\
\hline
\verb+chord.main.class.path+ & path & Classpath of Chord. It includes the path specified by property \verb+chord.java.analysis.path+ to allow running user-defined program analyses. & See \verb+${chord.main.dir}/build.xml+ \\
\hline
\verb+chord.bddbddb.class.path+ & path & Classpath of bddbddb. & See \verb+${chord.main.dir}/build.xml+ \\
\hline
\verb+chord.instr.agent.file+ & location & Shared library implementing Chord instrumentation agent. & \verb+${chord.main.dir}/lib/libchord_instr_agent.so+ (on Linux; \verb+.dll+ on Windows and \verb+.dylib+ on MacOS)\\
\hline
\verb+chord.javadoc.url+ & string & URL of the Javadoc location of program analyses. It is used when publishing targets (i.e. when property \verb+chord.publish.targets+ is set to true). & \verb+http://chord.stanford.edu/javadoc/+ \\
\hline
\multicolumn{4}{l}{{\bf Chord boot properties}} \\
\hline
\verb+chord.work.dir+ & location & Working directory during Chord's execution. & current working directory \\
\hline
\verb+chord.props.file+ & location & Properties file loaded by \verb+${chord.main.dir}/build.xml+.  Any of the below properties, as well as other user-defined properties to be passed to Chord (e.g. for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \verb+chord.<...>.path+ set in this file is converted to an absolute path element with respect to the directory containing this file. & \verb+${chord.work.dir}/chord.properties+ \\
\hline
\verb+chord.max.heap+ & string & Maximum memory size of JVM running Chord. & \verb+1024m+ \\
\hline 
\verb+chord.max.stack+ & string & Maximum thread stack size of JVM running Chord. & \verb+32m+ \\
\hline
\verb+chord.jvmargs+ & string & Arguments passed to JVM running Chord. & \verb+"-showversion -ea -Xmx${chord.max.heap} -Xss${chord.max.stack}"+ \\
\hline
\verb+chord.bddbddb.max.heap+ & string & Maximum memory size of JVM running bddbddb. & \verb+1024m+ \\
\hline
\multicolumn{4}{l}{{\bf Chord task properties}} \\
\hline
\verb+chord.build.scope+ & bool & Compute program scope (i.e. reachable classes and methods) using algorithm specified by properties \verb+chord.scope.kind+ and \verb+chord.reuse.scope+.  Program scope is computed regardless of the value of this property if another task (e.g. a program analysis to be run) needs it. & \verb+false+ \\
\hline
\verb+chord.run.analyses+ & string list & List of names of program analyses to be run in order. & \verb+""+ \\
\hline
\verb+chord.print.rels+ & string list & List of names of program relations whose contents must be printed to files \verb+${chord.out.dir}/<...>.txt+ where \verb+<...>+ denotes the relation name. & \verb+""+ \\
\hline
\verb+chord.publish.targets+ & bool & Publish all targets defined by program analyses in paths specified by properties \verb+chord.java.analysis.path+ and \verb+chord.dlog.analysis.path+. & \verb+false+ \\
\hline
\multicolumn{4}{l}{{\bf Basic program properties}} \\
\hline
\verb+chord.main.class+ & class & Fully-qualified name of main class of given program (e.g. \verb+com.example.Main+). &  \\
\hline
\verb+chord.class.path+ & path & Classpath of given program. \verb+${sun.boot.class.path}+ is implicitly appended to it. & \verb+${sun.boot.class.path}+ \\
\hline
\verb+chord.src.path+ & path & Java source path of given program. & \verb+""+ \\
\hline
\verb+chord.run.ids+ & string list & List of IDs to identify runs of given program. & \verb+0+ \\
\hline
\verb+chord.args.XXX+ & string & Command-line argument string to be used for given program in run having ID \verb+XXX+. & \verb+""+ \\
\hline
\verb+chord.runtime.jvmargs+ & string & Arguments to JVM when running given program.  It is used when the program is executed to compute its scope (i.e. when property \verb+chord.scope.kind+ is set to \verb+dynamic+) as well as when the instrumented program is executed for dynamic analyses. & \verb+"-ea -Xmx1024m"+ \\ 
\hline
\multicolumn{4}{l}{{\bf Program scope properties}} \\ 
\hline
\verb+chord.scope.kind+ & [\verb+rta+|\verb+dynamic+] & Algorithm to compute program scope (i.e. reachable classes and methods).  Current choices include \verb+rta+ (static Rapid Type Analysis) and \verb+dynamic+ (dynamic analysis). & \verb+rta+ \\
\hline
\verb+chord.reuse.scope+ & bool & Treat program scope as the classes and methods listed in files specified by properties \verb+chord.classes.file+ and \verb+chord.methods.file+, respectively. Property \verb+chord.scope.kind+ is ignored if this property is set to \verb+true+ and the two files exist. & \verb+false+ \\
\hline
\verb+chord.check.exclude+ & string list & List of prefixes of names of classes and packages to be excluded by program analyses. Interpretation of this property is analysis-specific. & \verb+"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."+ \\
\hline
\verb+chord.instr.exclude+ & string list & List of prefixes of names of classes and packages to be excluded from being instrumented.  Classes in package \verb+java.lang.ref+ are not instrumented regardless of the value of this property. & \verb+"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."+ \\
\hline
\multicolumn{4}{l}{{\bf Program analysis properties}} \\
\hline
\verb+chord.java.analysis.path+ & path & Classpath containing program analyses written in Java (i.e. \verb+@Chord+-annotated classes). & \verb+${chord.main.dir}/classes/+ \\
\hline
\verb+chord.dlog.analysis.path+ & path & Path of directories containing program analyses written in Datalog (i.e. \verb+*.datalog+ and \verb+*.dlog+ files). & \verb+${chord.main.dir}/src/dlog/+ \\
\hline
\verb+chord.reuse.rels+ & bool & Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. & \verb+false+ \\
\hline
\verb+chord.publish.results+ & bool & Publish the results of program analyses in HTML. Interpretation of this property is analysis-specific. & \verb+true+ \\
\hline
\multicolumn{4}{l}{{\bf Program transformation properties}} \\
\hline
\verb+chord.ssa+ & bool & Do SSA transformation for all methods deemed reachable by the algorithm used to compute program scope. & \verb+true+ \\
\hline
\multicolumn{4}{l}{{\bf Chord debug properties}} \\
\hline
\verb+chord.bddbddb.noisy+ & bool & Make bddbddb output debug info when solving Datalog programs. & \verb+false+ \\
\hline
\verb+chord.save.maps+ & bool & Write to file \verb+${chord.bddbddb.work.dir}/<...>.map+ when saving program domain named \verb+<...>+ (useful for debugging Datalog programs using \verb+debug+ target of \verb+${chord.main.dir}/build.xml+). & \verb+true+ \\
\hline
\multicolumn{4}{l}{{\bf Chord instrumentation properties}} \\
\hline
\verb+chord.trace.pipe+ & bool & Implement the dynamic trace file as a POSIX pipe instead of a regular file. & \verb+true+ \\
\hline
\verb+chord.trace.block.size+ & int & Number of bytes to read/write in a single operation from/to the dynamic trace file. & \verb+4096+ \\
\hline
\verb+chord.runtime.class+ & class & Subclass of \verb+chord.project.Runtime+ used by dynamic program analyses to handle events generated during an instrumented program's execution. & \verb+chord.project.BufferedRuntime+ \\
\hline
\hline
\multicolumn{4}{l}{{\bf Chord output properties}} \\
\hline
\verb+chord.out.dir+ & location & Directory to which Chord dumps all files. & \verb+${chord.work.dir}/chord_output/+ \\
\hline
\verb+chord.out.file+ & location & File to redirect standard output stream during Chord's execution. & \verb+${chord.out.dir}/log.txt+ \\
\hline
\verb+chord.err.file+ & location & File to redirect standard error stream during Chord's execution. & \verb+${chord.out.dir}/log.txt+ \\
\hline
\verb+chord.classes.file+ & location & File from/to which list of classes deemed reachable is read/written. & \verb+${chord.out.dir}/classes.txt+ \\
\hline
\verb+chord.methods.file+ & location & File from/to which list of methods deemed reachable is read/written. & \verb+${chord.out.dir}/methods.txt+ \\
\hline
\verb+chord.bddbddb.work.dir+ & location & Directory used by bddbddb as its input/output directory. & \verb+${chord.out.dir}/bddbddb/+ \\
\hline
\verb+chord.boot.classes.dir+ & location & Directory containing instrumented JDK classes used by given program. & \verb+${chord.out.dir}/boot_classes/+ \\
\hline
\verb+chord.user.classes.dir+ & location & Directory containing instrumented non-JDK classes of given program. & \verb+${chord.out.dir}/user_classes/+  \\
\hline
\verb+chord.instr.scheme.file+ & location & File specifying kind and format of events in dynamic trace file. & \verb+${chord.out.dir}/scheme.ser+ \\
\hline
\verb+chord.crude.trace.file+ & location & Crude dynamic trace file. & \verb+${chord.out.dir}/crude_trace.txt+ \\
\hline
\verb+chord.final.trace.file+ & location & Final dynamic trace file. & \verb+${chord.out.dir}/final_trace.txt+
\end{tabular}
\end{center}
\end{table}

\texonly{\newpage}
\section{Acknowledgments}

Chord would not be possible without the following open-source software:

\begin{itemize}
\item
\xlink{Joeq}{http://joeq.sourceforge.net/}, a Java compiler framework
\item
\xlink{Javassist}{http://www.csg.is.titech.ac.jp/~chiba/javassist/}, a Java bytecode manipulation tool
\item
\xlink{bddbddb}{http://bddbddb.sourceforge.net/}, a BDD-based Datalog solver
\end{itemize}

Chord additionally uses the following open-source tools and libraries:
\begin{itemize}
\item
\xlink{Ant-Contrib}{http://ant-contrib.sourceforge.net/}, a collection of useful Ant tasks  
\item
\xlink{BuDDy}{http://buddy.sourceforge.net/}, a BDD library
\item
\xlink{GNU Trove}{http://trove4j.sourceforge.net/}, a primitive collections library for Java
\item
\xlink{Java2HTML}{http://www.java2html.com/} and \xlink{Java2Html}{http://www.java2html.de/}, Java to HTML tools
\item
\xlink{Saxon}{http://saxon.sourceforge.net/}, an XSLT processor
\end{itemize}

Chord was supported in part by grants from the National Science Foundation, an equipment grant from Intel, and a Microsoft fellowship during 2005-2007.

@@

Given the program's application classpath via system property {\tt chord.app.class.class}
and either the program's main class via system property {\tt chord.main.class} or
the program's root methods via system property {\tt chord.root.classes}
(and, optionally, system properties {\tt chord.include.root.methods}
and {\tt chord.exclude.root.methods}),
\Chord\ uses system property {\tt chord.program.builder.class} to locate the
builder to be used for building an intermediate representation of the program,
namely, an object of class {\tt chord.program.Program}.
By default, the value of this property is class {\tt chord.program.builders.SootProgramBuilder}
which uses the Soot Java compiler framework \cite{Soot}.
Any builder, however, must implement interface
{\tt chord.program.builders.IProgramBuilder}.

@@

\texonly{\newpage}
\section{Executing Targets}

@@

\texonly{\newpage}
\section{Chord System Properties}
\label{sec-sys-props}

@@

\item
{\tt chord.program.file}

@@

\item
{\tt chord.app.class.path}

The application classpath of the program to be analyzed (as opposed to the
JDK library classpath which consists of jar files {\tt rt.jar}, {\tt jsse.jar}, and
{\tt jce.jar} and is implicitly appended to the program's application classpath to
yield the complete program classpath).

@@

This system property (and either {\tt chord.main.class} or {\tt chord.root.classes}) must
be defined if system property {\tt chord.program.file}
does not specify the file containing the serialized form of the intermediate representation
of the program to be analyzed.

The fully-qualified name of the main class (e.g., {\tt com.example.Main}) of the
program to be analyzed if the program is a complete one.

This system property (and {\tt chord.app.class.path})
must be defined if system property {\tt chord.program.file}
does not specify the file containing the serialized form of the intermediate representation
of the program to be analyzed.

\item
{\tt chord.root.classes}

A space-separated list of fully-qualified names of classes (e.g., {\tt com.example.Main})
whose public methods must be regarded as root methods (i.e., entry points) if the program
is an incomplete one.

This system property (and {\tt chord.app.class.path} plus, optionally,
system properties {\tt chord.include.root.methods} and {\tt chord.exclude.root.methods})
must be defined if system property {\tt chord.program.file}
does not specify the file containing the serialized form of the intermediate representation
of the program to be analyzed.

\item
{\tt chord.include.root.methods}

A space-separated list of fully-qualified signatures of
methods (e.g., {\tt com.example.Foo.bar(int,com.example.Baz[])}) that must be included
into the set of root methods (i.e., entry points)
if the program is an incomplete one.

\item
{\tt chord.exclude.root.methods}

A space-separated list of fully-qualified signatures of
methods (e.g., {\tt com.example.Foo.bar(int,com.example.Baz[])}) that must be excluded
from the set of root methods (i.e., entry points)
if the program is an incomplete one.

\item
{\tt chord.java.src.path}

@@

\item
{\tt chord.dlogmap.path}

@@

@@

\item
{\tt chord.trgts}
